Continuous Generalization of Buildings

### 2017-03-14 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
finished implementing a rough idea about continuous building generalization

\section{Introduction}
\label{sec:Introduction}

>>>>

\section{An idea of continuously generalising buildings}
We have an input map at scale $1:15 \mathrm{k}$.
We want to generate, by generalisation, $10$ maps which are at 
scale $1:20\mathrm{k}$, $1:25\mathrm{k}$, 
$1:30\mathrm{k}$, $\dots$, $1:65\mathrm{k}$.
We always produce a map by generalising the 
immediate-larger-scale map. For example, we produce the map at 
scale $1:25\mathrm{k}$ by generalising, instead of the input 
map, the map at scale $1:20\mathrm{k}$.
This production 
guarantees consistency. Namely, if a building does not exist on 
a map at a certain scale, then the building will never exist on 
a map at a smaller scale.

We have two requirements for an output map.
The first one is that the distance between two 
buildings should be at least $d_i=0.2 \mathrm{mm}/S_i$, where 
$S_i$ is the scale of map $i$.
The second requirement is that a building with area less than 
$A_i=0.16\mathrm{mm}^2/S^2_i$ should be eliminated. Roughly, a 
building with width less than 
$w_i=\sqrt{A_i}=0.4\mathrm{mm}/S$ should be eliminated.
In order to make sure that some small buildings will be 
eliminated, the radius $r_i$ that we use to buffer buildings 
should be smaller than $\frac{1}{2}w_i$. We simply use 
$r_i=\frac{1}{4}w_i$.
Our buildings may have been buffered with radius, in total, 
$r_{i-1}$ from previous steps.
Therefore, we only need to buffer with radius $r_i-r_{i-1}$ at 
the new 
step.

Our generalisation is as follows. We buffer buildings with 
radius $\frac{1}{2}d_i+r_i-r_{i-1}$, and merge the buffers 
overlapping 
each 
other.
Then we buffer the results with $-\frac{1}{2}d_i$.
In order to 
remove some spikes from the buffering, we buffer the new results 
with $-\epsilon_i$, and then again with $\epsilon_i$. We simply 
set 
$\epsilon_i=\frac{1}{10}(r_i-r_{i-1})$. After these buffering 
operations, we 
eliminate the buildings with area less than $d^2_i$.
